---
title: "Figure in publication"
output: 
  rmarkdown::html_vignette:
    code_folding: hide
vignette: >
  %\VignetteIndexEntry{Figure in publication}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Overview
This vignette replicates Figure 3 in [].

# R packages
```{r setup, warning = FALSE, message = FALSE,error=FALSE}
library(swim)
library(zen4R) #to access SWIM example shapefiles stored on Zenodo
library(terra)
library(ggplot2)
library(tidyterra)
library(patchwork)
```

# Load SWIM example shapefiles
These files are stored on Zenodo at https://zenodo.org/records/18165445.
```{r }
sw_example_shapefiles(FALSE) #TRUE will create a folder to save these files in your working directory

rm(coast_coarse)#We only need some of them for this vignette

ls()

# crop the buffer shapefiles to the nafo shapefile
buffer10<-crop(buffer10,nafo_4t)
buffer30<-crop(buffer30,nafo_4t)
buffer50<-crop(buffer50,nafo_4t)
```

# Assign events to spatial grid cells.
The example data file `sampling.weights` contains a column of spatial grid cell identities and a column of sampling weights according to distance buffers.
```{r }
head(sampling.weights)
```

Use function `sw_sample` to assign 10,000 events to spatial grid cells.
```{r }
set.seed(12345)

len=10000

x1<-sw_sample(len,sampling.weights,option=1)#Option 1 = based on weighted random sampling

x2<-sw_sample(len,sampling.weights,option=2)#Option 2 = distribute over ALL grid cells according to weight

x3<-sw_sample(len,sampling.weights,option=3)#Option 3 = distribute over ALL grid cells evenly

```

Compare outputs from the three options.
```{r }
head(x1)

x2

x3
```

# Plot 1
```{r }
#tally per hex
x1b<-cbind.data.frame(table(x1))
names(x1b)<-c('OBJECTID','count') #use same grid cell identity column header as shapefile
head(x1b)

grid.1b<-merge(ref_grid,x1b)

pl1<-ggplot()+
    geom_spatvector(data=nafo_4t,fill='white')+
    geom_spatvector(data=grid.1b,aes(fill=count),col=NA)+
    geom_spatvector(data=buffer10,fill=NA,col='black',linewidth=0.5,linetype=4)+
    geom_spatvector(data=buffer30,fill=NA,col='black',linewidth=0.5,linetype=3)+
    geom_spatvector(data=buffer50,fill=NA,col='black',linewidth=0.5,linetype=2)+
    scale_fill_viridis_c(name='Events',option='viridis',direction=-1,
                         limits=c(0.01,8.05),
                         begin = 0,end = 0.95)+
    geom_spatvector(data=nafo_4t,fill=NA)
```


# Plot 2
```{r }
names(x2)[3]<-'count'
grid.2<-ref_grid
grid.2$count<-0
buffers<-list(buffer50,buffer30,buffer10)#km
counts<-c(0.05,0.41,1.89)
for(i in 1:length(buffers)){
  buf<-vect(buffers[i])
  index<-intersect(buf,grid.2)
  grid.2[which(grid.2$OBJECTID%in%index$OBJECTID),'count']<-counts[i]
  }

grid.2<-grid.2[which(grid.2$count>0),]
label2<-rev(round(unique(grid.2$count),2))

pl2<-ggplot()+
    geom_spatvector(data=nafo_4t,fill='white')+
    geom_spatvector(data=grid.2,aes(fill=factor(count)),col=NA)+
    scale_fill_viridis_d(name='Events',option='viridis',direction=-1,
                         labels=label2,
                         begin = 0,end = 0.95)+
    guides(fill = guide_legend(reverse = TRUE))+
    geom_spatvector(data=buffer10,fill=NA,col='black',linewidth=0.5,linetype=4)+
    geom_spatvector(data=buffer30,fill=NA,col='black',linewidth=0.5,linetype=3)+
    geom_spatvector(data=buffer50,fill=NA,col='black',linewidth=0.5,linetype=2)+
    geom_spatvector(data=nafo_4t,fill=NA)
```


# Plot 3
```{r }
x3
grid.3<-ref_grid
grid.3$count<-x3[,2]

label3<-round(unique(grid.3$count),2)

pl3<-ggplot()+
    geom_spatvector(data=grid.3,aes(fill=factor(count)),col=NA)+
    scale_fill_viridis_d(name='Events',option='viridis',direction=-1,
                         begin = 0,end = 0.95,
                         label=label3)+
    geom_spatvector(data=nafo_4t,fill=NA)
```

# Combine
Set up
```{r }
CRS<-'epsg:4269'

map.theme<-list(coord_sf(crs=CRS,xlim=c(-71,-60),ylim=c(45.55,49.5)),
                theme(panel.grid.major = element_blank(),
                      panel.grid.minor = element_blank(),
                      axis.text = element_blank(),  # Remove axis text
                      axis.ticks = element_blank(), # Remove axis ticks
                      axis.title = element_blank()  # Remove axis titles
                ),
                theme(
                  legend.title = element_text(size = 13),
                  legend.position = "right",
                  legend.text = element_text(size = 12),
                  legend.key.size = unit(1, "cm"),
                  legend.justification = "left",
                  legend.box.margin = margin(l = 0.05, unit = "cm")   ))
```

Plot
```{r, fig.width=6, fig.height=8,out.width="100%"}
(big.plot<-(pl1+map.theme+ggtitle('SWIM Option 1'))/(pl2+map.theme+ggtitle("SWIM Option 2"))/pl3+map.theme+ggtitle("Without sampling weights"))
```

